Spatial Reasoning and Data Displays

### 2015-06-27 Paper/InfoVis2015Revision/TestingVisualAptitude.Rnw
Removing newtext, merge conflict

Each of the three sets of 20 lineups was taken from previous experiments \cite{loy:2015, roy2011visual} examining which type of plot most effectively conveyed important characteristics of the underlying data set. %\hhnote{citations?}
\begin{figure*}[htbp]\centering
\subfloat[Set 1: Boxplot]{
  \includegraphics[keepaspectratio=T,width=.245\linewidth]{../../Images/Lineups1/boxplot_1_15_5_4_13}}
\subfloat[Set 1: Density plot]{
  \includegraphics[keepaspectratio=T,width=.245\linewidth]{../../Images/Lineups1/density_1_15_5_4_13}}
\subfloat[Set 1: Dotplot ]{
  \includegraphics[keepaspectratio=T,width=.245\linewidth]{../../Images/Lineups1/dotplot_1_15_5_4_13}}
\subfloat[Set 1: Histogram]{
  \includegraphics[keepaspectratio=T,width=.245\linewidth]{../../Images/Lineups1/histogram_1_15_5_4_13}}\\
\subfloat[Set 2: Boxplot]{
  \includegraphics[keepaspectratio=T,width=.245\linewidth]{../../Images/Lineups2/file147f94f6965d7}}
\subfloat[Set 2: Boxplot with jittered points]{
  \includegraphics[keepaspectratio=T,width=.245\linewidth]{../../Images/Lineups2/file147f9e65f0e4}}
\subfloat[Set 2: Bee swarm boxplot]{
  \includegraphics[keepaspectratio=T,width=.245\linewidth]{../../Images/Lineups2/file147f9fc58d73}}
\subfloat[Set 2: Violin plot]{
  \includegraphics[keepaspectratio=T,width=.245\linewidth]{../../Images/Lineups2/file147f93acbb7e4}}\\
\subfloat[Set 3: QQ-plot with guide line]{
  \includegraphics[keepaspectratio=T,width=.245\linewidth]{../../Images/Lineups3/file13876a225d34-single}}
\subfloat[Set 3: QQ-plot with acceptance bands]{
  \includegraphics[keepaspectratio=T,width=.245\linewidth]{../../Images/Lineups3/file13877c93dc78-single}}
\subfloat[Set 3: QQ-plot rotated 45 degrees.]{
  \includegraphics[keepaspectratio=T,width=.245\linewidth]{../../Images/Lineups3/file13878e5c92f-single}}
\protect\caption{Lineup plot types used in the experiment. \label{fig:lineups} Each set of plots is representative of the plot types shown in a block of lineups in the experiment, and each block represents a subset of plots from a traditional lineup experiment to determine which visualization method facilitates identification of the plot with the strongest visual signal. Set 1 manipulates group means and variance, set 2 manipulates group means, and set 3 examines violations of normality. These tasks were chosen as common statistical visualization tasks, and while not exhaustive, should provide a broad basis for interpreting the results of this experiment.}
\end{figure*}

@@

\paragraph{Experimental Procedure}
All tasks (cognitive and lineups) were provided to participants on paper \newtext{in a supervised lab setting}, to conform to the procedure used in~\cite{ekstrom1976manual}. The order of tasks was the same for each participant due to the constraints of in-person testing; an internal pilot study did not indicate an effect of task order, \newtext{nor did the pilot results suggest an interaction/learning effect from one task to the next.}

@@

After each test or block of lineups, participants were given 1-2 minutes to rest and recover; the order of tests was designed to prevent fatigue on a single task \newtext{(which led us to interweave lineup evaluations)}. The duration of testing for each participant was approximately 1 hour. \newtext{None of the participants who showed up for their scheduled session asked to leave early.} A set of test documents (with copyrighted material redacted) is available as supplemental materials.

>>>>

Each of the three sets of 20 lineups was taken from previous experiments \cite{loy:2015, roy2011visual} examining which type of plot most effectively conveyed important characteristics of the underlying data set. %\hhnote{citations?}

\begin{figure*}[htbp]\centering
\subfloat[Set 1: Boxplot]{
  \includegraphics[keepaspectratio=T,width=.245\linewidth]{../../Images/Lineups1/boxplot_1_15_5_4_13}}
\subfloat[Set 1: Density plot]{
  \includegraphics[keepaspectratio=T,width=.245\linewidth]{../../Images/Lineups1/density_1_15_5_4_13}}
\subfloat[Set 1: Dotplot ]{
  \includegraphics[keepaspectratio=T,width=.245\linewidth]{../../Images/Lineups1/dotplot_1_15_5_4_13}}
\subfloat[Set 1: Histogram]{
  \includegraphics[keepaspectratio=T,width=.245\linewidth]{../../Images/Lineups1/histogram_1_15_5_4_13}}\\
\subfloat[Set 2: Boxplot]{
  \includegraphics[keepaspectratio=T,width=.245\linewidth]{../../Images/Lineups2/file147f94f6965d7}}
\subfloat[Set 2: Boxplot with jittered points]{
  \includegraphics[keepaspectratio=T,width=.245\linewidth]{../../Images/Lineups2/file147f9e65f0e4}}
\subfloat[Set 2: Bee swarm boxplot]{
  \includegraphics[keepaspectratio=T,width=.245\linewidth]{../../Images/Lineups2/file147f9fc58d73}}
\subfloat[Set 2: Violin plot]{
  \includegraphics[keepaspectratio=T,width=.245\linewidth]{../../Images/Lineups2/file147f93acbb7e4}}\\
\subfloat[Set 3: QQ-plot with guide line]{
  \includegraphics[keepaspectratio=T,width=.245\linewidth]{../../Images/Lineups3/file13876a225d34-single}}
\subfloat[Set 3: QQ-plot with acceptance bands]{
  \includegraphics[keepaspectratio=T,width=.245\linewidth]{../../Images/Lineups3/file13877c93dc78-single}}
\subfloat[Set 3: QQ-plot rotated 45 degrees.]{
  \includegraphics[keepaspectratio=T,width=.245\linewidth]{../../Images/Lineups3/file13878e5c92f-single}}
\protect\caption{Lineup plot types used in the experiment. \label{fig:lineups} Each set of plots is representative of the plot types shown in a block of lineups in the experiment, and each block represents a subset of plots from a traditional lineup experiment to determine which visualization method facilitates identification of the plot with the strongest visual signal. Set 1 manipulates group means and variance, set 2 manipulates group means, and set 3 examines violations of normality. These tasks were chosen as common statistical visualization tasks, and while not exhaustive, should provide a broad basis for interpreting the results of this experiment.}
\end{figure*}

@@

\paragraph{Experimental Procedure}
All tasks (cognitive and lineups) were provided to participants on paper in a supervised lab setting, to conform to the procedure used in~\cite{ekstrom1976manual}. The order of tasks was the same for each participant due to the constraints of in-person testing; an internal pilot study did not indicate an effect of task order, nor did the pilot results suggest an interaction/learning effect from one task to the next.

@@

After each test or block of lineups, participants were given 1-2 minutes to rest and recover; the order of tests was designed to prevent fatigue on a single task (which led us to interweave lineup evaluations). The duration of testing for each participant was approximately 1 hour. None of the participants who showed up for their scheduled session asked to leave early. A complete set of test documents (with copyrighted material redacted) is available as supplemental materials.
